I would like to thank my primary supervisor Alex Singleton for his continuous support throughout my PhD. Alex was instrumental in shaping the outputs of this thesis, ensuring I remained focussed on my research goals, and always providing valuable feedback. I would also like to thank my secondary supervisor Alessia Calafiore, for providing feedback that has helped shape the thesis into its current form. Alessia always provided a unique perspective towards my research, that proved invaluable in maintaining my motivation to develop my research ideas. I would also like to thank Jeremy Morley from Ordnance Survey, who always showed interest and support throughout my PhD project. Thank you also to UKRI (ESRC), Ordnance Survey and the Data Analytics and Society Centre for Doctoral Training for financially supporting this project.

Thank you to everyone at the Geographic Data Science Lab for providing continued support throughout my PhD. Countless discussions both online and in person have helped develop my knowledge and shape the outputs of this thesis.

Thank you to my parents who have supported me throughout my life and the various changes in direction I have taken over the years, and thank you to James Collins and Nathan Wood, for all the long distance chats that kept me sane throughout COVID.

Most of all, thank you to Jenny. Without your love and support I would not have been able to complete this thesis. Thank you for always being there for me, and for always believing in me.
